An efficient feedback calibration algorithm for direct imaging radio telescopes

### 2016-03-01 cal_demo/ms.tex
addressing more of nithyas comments

An important feature to note is that, like the MOFF-generated images themselves, equation~\ref{eq:cal_solution} includes the antenna auto-correlations (the sum is over \emph{all} $b$, not excluding $a$). It can be difficult to perfectly model the noise bias from auto-correlations, which can often times be far brighter than the visibilities themselves. It can therefore be beneficial to subtract this term directly from \Cna, and exclude the $b=a$ term in the sum.
\begin{equation}
\Cna \rightarrow \Cna - \frac{1}{\Nant\, g^{*(n)}_a} \beamtheta^*_a(\spix) e^{-2\pi i \spix \cdot \ra} \left<|\Er{a}|^2\right>_t
\end{equation}
This requires generating these correlations, which again only scale as $\mathcal{O}(\Nant)$, and are generally useful for array diagnostics. ({\bf What happened to the $g_a^T$ term outside the sum? And why did you drop $\hat{\mathbf{s}}_0$ in $W_a^*$}?)

We conclude this section by connecting our calibration expression to that found in a visibility framework. In the limit of a single bright calibrating source at phase center, we can greatly simplify equations~\ref{eq:cna} and~\ref{eq:cal_solution}. We will assume the beams are normalized such that $\beamtheta(0)=1$. We can further drop the exponential phase terms because $\spix=0$. We then absorb the true gains and gain corrections into the true visibilities in equation~\ref{eq:cna} to express as a sum of measured visibilities.
\begin{equation}
\mathcal{C}^{(n)}_{a,0} \rightarrow \frac{1}{\Nant}\sum_b \frac{1}{g^{*(n)}_b} \V_{ab}
\end{equation}
({\bf It is not clear what happened to the $g$ terms.})

>>>>

An important feature to note is that, like the MOFF-generated images themselves, equation~\ref{eq:cal_solution} includes the antenna auto-correlations (the sum is over \emph{all} $b$, not excluding $a$). It can be difficult to perfectly model the noise bias from auto-correlations, which can often times be far brighter than the visibilities themselves. It can therefore be beneficial to subtract this term directly from \Cna, and exclude the $b=a$ term in the sum.
\begin{equation}
\Cna \rightarrow \Cna - \frac{1}{\Nant\, g^{*(n)}_a} \beamtheta^*_a(\spix) e^{-2\pi i \spix \cdot \ra} \left<|\Er{a}|^2\right>_t
\end{equation}
We have absorbed $g_a^T$ into the electric field so that the correlation is now simply the autocorrelation of the uncalibrated antenna measurement. This requires generating these correlations, which again only scale as $\mathcal{O}(\Nant)$, and are generally useful for array diagnostics.

We conclude this section by connecting our calibration expression to that found in a visibility framework. In the limit of a single bright calibrating source at phase center, we can greatly simplify equations~\ref{eq:cna} and~\ref{eq:cal_solution}. We will assume the beams are normalized such that $\beamtheta(0)=1$. We can further drop the exponential phase terms because $\spix=0$. We then absorb the true gains into the true visibilities in equation~\ref{eq:cna} to express as a sum of measured, uncalibrated, visibilities.
\begin{equation}
\mathcal{C}^{(n)}_{a,0} \rightarrow \frac{1}{\Nant}\sum_b \frac{1}{g^{*(n)}_b} \V_{ab}
\end{equation}
